---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Olivia Zhang"
date: "03/26/2025"
output: github_document
---

## Load Packages and Data  

Load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

Now, load the dataset.

```{r load-data, message = FALSE}
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = as.numeric(str_remove(date, "\\)"))) %>%
  select(title, artist, year, link)  
```


## Exercise 10  

The warnings mean that: 1) there are some missing values in the date column, which is normal, because not all names have dates come after them; 2) not everything following the names in parentheses consists of years or numbers, so the as.numeric function doesn’t work for all items in the year info. It only works for items that contain only numeric years without additional strings. 


## Exercise 11  

```{r skim-uoe-art}
skim(uoe_art)
```

The artist info misses 111 data points, and the year info misses 1575 data points.

## Exercise 12

```{r hist-year}
uoe_art %>%
  ggplot(aes(x = year)) +
  geom_histogram(binwidth = 30)
```

There is one outlier that's closer to 0 that makes the x axis really stretched out.

## Exercise 13

```{r correct}
#find out the wrong year
table(uoe_art$year)
uoe_art %>% filter(year == 2)

#correct it 
uoe_art$year <- ifelse(uoe_art$year == 2, 1964, uoe_art$year)
#check
table(uoe_art$year)

#plot
uoe_art %>%
  ggplot(aes(x = year)) +
  geom_histogram(binwidth = 20)
```

The code didn't capture the correct year information because the original title was Death Mask (2) (1964), which confused the code to think that the first number after ( was the year we are looking for.

## Exercise 14

```{r artist}
uoe_art %>% 
  count(artist) %>%
  arrange(desc(n))
```

The most featured artist is "Unknown." I'm not sure why the university has so many pieces from Unknown artists, but I looked up in their website. They say: " The early stages of this collecting were closely linked with galvanising the institution’s identity and status as a place of learning and inspiration, through the commissioning and collecting of portraits and busts of Professors and key alumni." So I guess they may not know all the artists that created the portraits and busts.

## Exercise 15

```{r child}
child_count <- uoe_art %>%
  filter(
    str_detect(title, regex("child", ignore_case = TRUE))
  ) %>%
  count()
```

There are `r child_count` art pieces have the word "child" in their title.